---
title: "R Notebook"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(magrittr)
library(haven)

```

```{r}
nhanes17_18demo <- read_xpt("https://wwwn.cdc.gov/Nchs/Nhanes/2017-2018/DEMO_J.XPT")
nhanes18_18_30DayInterview <- read_xpt("https://wwwn.cdc.gov/Nchs/Nhanes/2017-2018/DSQIDS_J.XPT")
```

```{r}
nhanes17_18demo %>% colnames()
nhanes18_18_30DayInterview %>% colnames()
```

All survey respondents were eligible for 30 day dietary supplements interview. Hence, the total number of people who reported taking any supplements at all during the survey cycle 2017-2018 were as follows:


```{r}
nhanes17_18Supplements <- nhanes18_18_30DayInterview %>% 
  select(SEQN, DSDPID, DSDSUPP) %>%
  left_join(nhanes17_18demo %>% 
              select(SEQN, WTINT2YR),
            by = "SEQN")
```

```{r}
nhanes17_18Supplements %>% View()
```

Check to see how many SEQn are NA or missing

```{r}
sum(is.na(nhanes17_18Supplements$SEQN))
```
## None are missing

Sum of all weights - This indicates the number of products bought. Single person can have multiple supplements.
```{r}
sum(nhanes17_18Supplements$WTINT2YR) %>%
  format(big.mark   = "",   big.interval = 3L)
```
Supplements having calcium in their Names (DSDSUPP)
```{r}
nhanes17_18Supplements %>% 
  filter(str_detect(DSDSUPP, regex(pattern = "calcium", ignore_case = T)),
         !str_detect(DSDSUPP, regex(pattern = "antacid", ignore_case = T))) %>%
  group_by() %>%
  summarise(wt_sum = sum(WTINT2YR))
```
sums up to be 29,020,781. Redoing this to be sure

```{r}
sum(nhanes17_18Supplements$WTINT2YR[grepl(nhanes17_18Supplements$DSDSUPP,
                                          pattern = "calcium",
                                          ignore.case = T) &
                                      !grepl(nhanes17_18Supplements$DSDSUPP,
                                          pattern = "antacid",
                                          ignore.case = T)])
```
This matches with what the program outputs.

Getting the total number of supplements



```{r}
nhanes17_18Supplements %>%
  filter(str_detect(DSDSUPP, regex(pattern = "calcium", ignore_case = T)),
         !str_detect(DSDSUPP, regex(pattern = "antacid", ignore_case = T))) %>%
  summarise(totalSuppl = n_distinct(DSDPID),
            totalWeights = sum(WTINT2YR))
  
```






